%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins

\name{Ariana Swynenburg} % Your name
\address{ariana.swynenburg.com \\ linkedin.com/in/aswynenburg}
\address{(503)~$\cdot$~440~$\cdot$~3677 \\ ariana@swynenburg.com}

\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf Gonzaga University} \hfill {\em August 2012 - May 2016} \\ 
Bachelor of Arts in Economics \\
Bachelor of Arts in English Literature \smallskip \\

\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Experience}

\begin{rSubsection}{(Insight Global) Amazon}{March 2017- Present}{Recruiting Coordinator}{Seattle, WA}
\item Responsible for arranging and scheduling interviewers, travel accommodations, and catering for large-scale hiring events across North America. 
\item Communicate across various levels and departments within Amazon to facilitate interviews.
\item Responsible for keeping service level agreements with candidates (two and five day response windows).
\item Guide candidates throughout their entire interview experience at Amazon.
\item Balance and accomodate the needs of candidates, recruiters, and interviewers.
\item Establish the interviewer training program for the Mid Market Sales team to graduate more certified interviewers in order to meet the growing demand for interviewers.
\end{rSubsection}
	
%------------------------------------------------

\begin{rSubsection}{Cathy for Congress}{May 2016 - March 2017}{Field Director}{Spokane, WA}
\item Increased win margin by over 15,000 votes from 2014.
\item Hired, directed, and oversaw team of fifteen interns.
\item Organized grassroots events across one of the largest congressional districts.
\item Planned and coordinated doorbelling for 60,000 homes.
\item Ran the campaign's Twitter, Facebook, Instagram, and Snapchat social media accounts.
\item Wrote weekly debriefs for major-level (\$2,000+) donors.
\item Selected \textit{thank you} gifts for major-level donors and the GOP's largest fundraiser, Congresswoman McMorris Rodgers.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{U.S. House of Representatives}{September 2015 - December 2015}{Congressional Intern}{Spokane, WA}
\item Created and organized political binders and debriefings for future interns.
\item Answered questions and assisted constituents with government agencies and policy.
\item Worked as a point-of-contact between constituents and caseworkers.
\item Oversaw orders for flag requests for veteran funerals.
\end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Strengths}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Software & iCIMS, AmazonHIRE, Tableau, Intranet Quorum, CMDI, NationBuilder, Word \\
Hard Skils & Scheduling across timezones, event planning for 2,000+ attendees, budgeting and fundraising \\
Soft Skills & Leadership of diverse teams, interpersonal communication, conflict resolution
\end{tabular}

\end{rSection}

%----------------------------------------------------------------------------------------
%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------

%\begin{rSection}{Section Name}

%Section content\ldots

%\end{rSection}

%----------------------------------------------------------------------------------------

\end{document}
